{\itshape Depicting urban boundaries from a mobility network of spatial interactions: A case study of Great Britain with geo-located Twitter data}

### 2016-07-23 urban_boundaries_gb_IJGIS/IJGIS/Paper.tex
temp

\begin{abstract}
Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a spatial Twitter user interaction network that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.9\linewidth]{./figure/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) displacements longer than 10 km (b) displacements shorter than 4 km (c) and displacements longer than 4 km (d) The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed in black.}
\label{S5_Fig}
\end{center}
\end{figure}

@@

A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.
The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas, which is explained by the usual flight passenger routes.
The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
For example, East Barnet and West Enfield seem to have higher interactions than those resulted from in the emerging cohesive zone between the two boroughs.

@@

%\clearpage
\section{Discussions}

@@

\bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, pp. 2178-2199.
\end{thebibliography}

\bibliographystyle{tGIS}
%\bibliography{Twitter_Urban_Boundary}

\label{lastpage}

>>>>

\begin{abstract}
Existing urban boundaries are usually defined by government agencies for political and administrative purposes.
However, it is not clear whether the boundaries truly reflect people's interactions with the urban space in their intra- and inter-regional activities.
Defining urban boundaries which consider socio-economic relationships and citizen commute patterns is important for many aspects of urban planning.
In this study, we presented a method to redraw urban boundaries based upon human interactions with the physical space.
Specifically, we depicted the urban boundaries of Great Britain using a mobility network of Twitter user spatial interactions that was inferred from over 69 million geo-located Twitter messages.
We redrew the non-administrative anthropographic boundaries in a hierarchical fashion based on different physical movement ranges of users inferred from the collective mobility patterns of Twitter users in Great Britain.
The results of strongly connected urban regions in the form of communities in the network space yield geographically cohesive, non-overlapping urban areas, which provide a clear delineation of the non-administrative anthropographic urban boundaries of Great Britain.
The technique was applied to both national (Great Britain) and municipal scales (the London metropolis).
While our results corresponded well with the administrative boundaries, many unexpected and interesting boundaries were identified.
More importantly, as the depicted urban boundaries exhibited a strong instance of spatial proximity, we further employed a gravity model to connect human mobility research to understand and justify the distance decay effects in shaping the delineated urban boundaries.
This well fitted gravity model explains how geographical distances found in the mobility patterns affect the interaction strength among different non-administrative anthropographic urban areas, which provides a new understanding of the interactions between human activity and urban space.
\newline

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.9\linewidth]{./figure/S5_community}
\caption{{\bf The community structure from collective Twitter user displacements reveals non-administrative anthropographic urban boundaries} (a) all displacements with $L = 7.79$. (b) displacements longer than 10 km ($L=xx$) (c) displacements shorter than 4 km ($L=xx$) (d) and displacements longer than 4 km ($L=xx$).The partition of space was done using a 10 km fishnet to map the directed displacements from and to each cell. Each color represents a unique community with more Twitter users displacements among the cells compared to others. Major cities (urban audit functional areas) and NUTS are displayed in black.}
\label{S5_Fig}
\end{center}
\end{figure}

@@

A more detailed study was conducted over the greater London region revealing the intra-city spatial interaction patterns.

The spatial partitions derived from a fine grid of 1km using all available Twitter user trips without any restriction on trip distances yields geographic boundaries comparable to some of London's boroughs  (Fig.~\ref{S7_Fig}).
However, some areas are shown to be more cohesive and display greater spatial interactions across the administrative boundaries, for instance, central London.
Although, these results suggest that travelers seem to be localized over certain areas of the city most of the time, some regions do exhibit long distance interaction patterns.
For example, the separate geographic areas in the south of Hillingdon which includes Heathrow Airport exhibits more connectivity to central London than its surrounding areas, which is explained by the usual flight passenger routes.
The technique also reveals some of the emerging communities around the borders due to the spatial intermingling of both communities.
For example, East Barnet and West Enfield seem to have higher interactions than those resulted from in the emerging cohesive zone between the two boroughs.

@@

%\clearpage
\section{Discussions}
In this study,

@@

\bibitem[\protect\citeauthoryear{Zhong {\itshape{et~al.}}}{2014}]{zhong2014}
Zhong, C., Arisona, S.M., Huang, X., Batty, M., Schmitt, G., 2014. Detecting the dynamics of urban structure through spatial network analysis. International Journal of Geographical Information Science, 28, pp. 2178-2199.
\end{thebibliography}
\bibliographystyle{tGIS}
\label{lastpage}
